{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-29 paper/paper.tex
used names of the paper for the next properties
made next properties \small to fit in \textwidth
added note aboute \mapsto^*
corrected spelling
use new property names

\todo{Use names from paper}
\begin{enumerate}
\item $Dom(next) = \{i \in \mathcal{P} | se(i) = high \land \exists j \in \mathcal{P} . i \mapsto^* j \land se(j) \neq high\}$ \todo{use simple method of new paper?}
\item $i, j \in Dom(next) \land i \mapsto j \Rightarrow next(i) = next(j)$
\item $i \in Dom(next) \land j \not\in Dom(next) \land i \mapsto j \Rightarrow next(i) = j$
\item $j, k \in Dom(next) \land i \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = next(k)$ \todo{is there an error?}
\item $i, j \in Dom(next) \land k \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = k$
\end{enumerate}

Die domain of next just captures the high, but not always high program points (i.e. the ones
that can result in a hidden thread). The second property, states that two directly successive high
program points have the same program point in which the thread becomes visible again. The third rule
is the counterpart of the second: If a low program point follows a high program point, this low program
point is the result of the next function for the high program point.

>>>>

{\small
\begin{enumerate}
\item[NePd] $Dom(next) = \{i \in \mathcal{P} | se(i) = high \land \exists j \in \mathcal{P} . i \mapsto^* j \land se(j) \neq high\}$ \todo{use simple method of new paper?}
\item[NeP1] $i, j \in Dom(next) \land i \mapsto j \Rightarrow next(i) = next(j)$
\item[NeP2] $i \in Dom(next) \land j \not\in Dom(next) \land i \mapsto j \Rightarrow next(i) = j$
\item[NeP3] $j, k \in Dom(next) \land i \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = next(k)$ \todo{is there an error?}
\item[NeP4] $i, j \in Dom(next) \land k \not\in Dom(next) \land i \mapsto j \land i \mapsto k \land j \neq k \Rightarrow next(j) = k$
\end{enumerate}
}

where $\mapsto^*$ is the reflexive and transitive closure of $\mapsto$.

The domain of next (i.e. NePd) captures the high, but not always high program points (i.e. the ones
that can result in a hidden thread). The property NeP1, states that two directly successive high
program points have the same program point in which the thread becomes visible again. The property NeP2
is the counterpart of the NeP1: If a low program point follows a high program point, this low program
point is the result of the next function for the high program point.
